\documentclass{report}
\usepackage{hyperref} % For hyperlinks in the document
% chktex-file 44
% chktex-file 38
% chktex-file 8

\title{Home Security System Proposal}
\author{Your Name}
\date{\today}

\begin{document}

\maketitle

\tableofcontents
\newpage

\chapter{Description of Project}
\section{Project Idea}
This proposal is for a home security system that is a hardware and software solution.
Our company will offer installation services for the system, which is a base station and various POE IP cameras.
The storage for the system will be through AWS and there will be a web interface to access the recorded feeds.
The monetization will be through a hardware and install fee, and a monthly subscription fee for the AWS storage and web interface.

The hardware will be based of a Raspberry Pie 5, with a Corral Accelerator, and a POE switch.
It will all be contained within a custom case that will be mounted to the wall.
The cameras will be POE IP cameras that will be connected to the switch and powered by it.
The customer will be able to pick various numbers and variations of indoor and outdoor cameras.

The Pie will be running the default version of Raspbian.
The open source software Frigate will be used to manage the cameras, feeds, recordings, and detection.
The storage will be through AWS S3 mounted locally using Rclone.
Frigate will handle the web interface, but there will be a tunnel to the AWS instance so the customer can access the recordings on the web.

The install service will be done by in house contractors.
They will visit the customer's home, advise them on number of cameras and camera placement.
They will then install the hardware, connect it to the internet, and show the customer how to use the system.


\chapter{Likely Marketing Efforts}
\section{Target Audience}
Testing Testing Testing
\section{Cost Expectations}
Testing Testing Testing

\chapter{Technical Details / Technical Research}
A three-tier surveillance security system package specifically designed for family homes. 
The packages offer different levels of security, from essential home monitoring to advanced surveillance with AI-based detection. 
Each package includes necessary hardware, software, and storage solutions for easy installation and use. 
The Coral USB Accelerator is included in all packages to enhance AI-based motion detection and object recognition. 
Real pricing for PoE switches has also been incorporated. 
Camera specifications have been adjusted so that the first tier supports either indoor or outdoor use, and the second tier includes both indoor and outdoor cameras.

Tier 1: Essential Home Package
The Essential Home Package is designed for families looking for an entry-level yet effective surveillance system. 
This package includes two cameras that can be used either indoors or outdoors, providing flexibility for home security.
Components:
\begin{itemize}
    \item 2 Indoor/Outdoor PoE Cameras (Reolink 5MP, 2560$\times$1920 resolution, 30 fps) - \$70 each
    \item 1 Raspberry Pi 5 (4GB RAM) pre-installed with surveillance software - \$60
    \item 1 Coral USB Accelerator for AI-powered motion detection - \$25.99
    \item 1 PoE Switch (4-port TP-Link TL-SF1005P) - \$40
\end{itemize}
\textbf{Features:}
\begin{itemize}
    \item Local storage on Raspberry Pi 5 (up to 128GB via microSD)
    \item Mobile app access for live viewing
    \item AI-based motion detection and object recognition using Coral USB Accelerator
\end{itemize}
\textbf{Estimated Total Cost:} \$266

\textbf{Tier 2: Smart Home Package}

This package offers additional security coverage and smart features for homeowners seeking more control over their surveillance system. It includes a combination of indoor and outdoor cameras, ensuring comprehensive security coverage.

\textbf{Components:}
\begin{itemize}
    \item 2 Indoor PoE Cameras + 2 Outdoor PoE Cameras (Reolink 5MP, 2560$\times$1920 resolution, 30 fps) - \$70 each
    \item 1 Raspberry Pi 5 (4GB RAM) pre-installed with surveillance software - \$60
    \item 1 Coral USB Accelerator for AI-powered motion detection - \$25.99
    \item 1 PoE Switch (8-port NETGEAR GS308PP) - \$100
\end{itemize}
\textbf{Features:}
\begin{itemize}
    \item Local storage on Raspberry Pi 5 (up to 256GB via external SSD)
    \item Mobile app access for live viewing and playback
    \item AI-based human and vehicle recognition for smarter motion detection
\end{itemize}
\textbf{Estimated Total Cost:} \$506

\textbf{Tier 3: Advanced Family Package}

The Advanced Family Package is ideal for families wanting full security coverage with AI-based surveillance features and cloud storage options. This package includes six cameras that can be used in any combination of indoor or outdoor settings.

\textbf{Components:}
\begin{itemize}
    \item 6 Indoor/Outdoor PoE Cameras (Reolink 5MP, 2560$\times$1920 resolution, 30 fps) - \$70 each
    \item 1 Raspberry Pi 5 (8GB RAM) pre-installed with surveillance software - \$80
    \item 1 Coral USB Accelerator for AI-powered motion detection - \$25.99
    \item 1 PoE Switch (16-port TP-Link TL-SG1016PE) - \$180
\end{itemize}
\textbf{Features:}
\begin{itemize}
    \item Local storage on Raspberry Pi 5 (up to 512GB via external SSD)
    \item Mobile app access for live viewing, playback, and two-way audio
    \item AI-powered motion detection and object recognition using Coral USB Accelerator
    \item Optional cloud storage integration with AWS
\end{itemize}
\textbf{Estimated Total Cost:} \$826

\section{Staffing and Salaries}

\textbf{Department Director:} \$180k—\$200k/yr

\textbf{Software Team:}
\begin{itemize}
    \item \textbf{Business Analyst/Scrum Master:} \$115k—\$130k/yr
    \item \textbf{Software Dev Lead}
    \begin{itemize}
        \item \textbf{Team 1:}
        \begin{itemize}
            \item \textbf{Senior Dev:} \$110k—\$160k/yr
            \item \textbf{Junior Dev:} \$75k—\$90k/yr
            \item \textbf{Junior Dev:} \$75k—\$90k/yr
        \end{itemize}
        \item \textbf{Team 2:}
        \begin{itemize}
            \item \textbf{Senior Dev:} \$110k—\$160k/yr
            \item \textbf{Junior Dev:} \$75k—\$90k/yr
            \item \textbf{Junior Dev:} \$75k—\$90k/yr
        \end{itemize}
    \end{itemize}
\end{itemize}

\textbf{Systems Team:}
\begin{itemize}
    \item \textbf{Systems Administrator:} \$68k—\$120k/yr
    \item \textbf{Network and Security Lead:} \$120k—\$140k/yr
    \begin{itemize}
        \item \textbf{Network and Security Specialist:} \$100k—\$120k/yr
    \end{itemize}
    \item \textbf{Helpdesk Lead/External Liaison:} \$50k—\$60k/yr
    \begin{itemize}
        \item \textbf{Helpdesk Specialist:} \$30k—\$40k/yr
        \item \textbf{Helpdesk Specialist:} \$30k—\$40k/yr
        \item \textbf{Helpdesk Specialist:} \$30k—\$40k/yr
    \end{itemize}
\end{itemize}



\chapter{Defined Goals / MVP}
The end product is a home security system and hardware solution that we offer install services for. 
The package to the user will be home base station that has a POE switch, and varying IP cameras to connect to it. 
The storage for the system will be through AWS and the there will be a web interface to access the recorded feeds. 
The monetization is through a hardware and install fee, and a monthly subscription fee for the AWS storage and web interface. 
\chapter{Testing to be Performed}
\begin{tabular}{|l|l|l|l|}
\hline
Requirement & Test Case & Test Result & Defect/Error \\
\hline
Req 1 & Test Case 1 &  &  \\
\hline
Req 2 & Test Case 2 &  &  \\
\hline
Req 3 & Test Case 3 &  &  \\
\hline
Req 4 & Test Case 4 &  &  \\
\hline
Req 5 & Test Case 5 &  &  \\
\hline
Req 6 & Test Case 6 &  &  \\
\hline
Req 7 & Test Case 7 &  &  \\
\hline
Req 8 & Test Case 8 &  &  \\
\hline
Req 9 & Test Case 9 &  &  \\
\hline
Req 10 & Test Case 10 &  &  \\
\hline
Req 11 & Test Case 11 &  &  \\
\hline
Req 12 & Test Case 12 &  &  \\
\hline
Req 13 & Test Case 13 &  &  \\
\hline
Req 14 & Test Case 14 &  &  \\
\hline
Req 15 & Test Case 15 &  &  \\
\hline
Req 16 & Test Case 16 &  &  \\
\hline
Req 17 & Test Case 17 &  &  \\
\hline
Req 18 & Test Case 18 &  &  \\
\hline
Req 19 & Test Case 19 &  &  \\
\hline
Req 20 & Test Case 20 &  &  \\
\hline
\end{tabular}

\chapter{Summary of Proposal}
Many homeowners would love to have security for their house. 
Our product does not only allow for this security but is also more advanced than competitors.
With the 


\chapter{Timeline and Budget}
\section{Timeline}

\section{Budget Estimates}
Cost estimates are divided into hardware, 
storage/software, licensing, human resources,
developer labor, installer labor, employee benefits, 
vehicle cost, and damage allowance.

Hardware consists of the Pi 5, costing \$150 dollars (including shipping). Cameras, 
the average customer will buy 4 1080p cameras valued at 100 dollars each. 
The Coral TPU and the M2 accelerator key cost \$100 together.
The POE switch will cost 50 dollars, and another 50 dollars for cabling, mounting equipment, etc.

Storage cost refers to the AWS storage cost for 4 cameras in 1080p, with the predetermined storage. This is estimated to be \$96,000 a year.
Software is \$0 outside of storage costs.
Licensing includes electrical contractor licenses for 3 installers, \$600. Business license, \$100. 
Home Improvement Contractor license. \$1095.
\begin{tabular}{|l|c|}
\hline
Item & Cost \\
\hline
Hardware & \$1,200,000 \\
Software & \$0 AWS bills to the customer for storage and interface. \\
Licensing & \$200 electrical contractor licenses for 3 installers. \$600 \\
Human Resources & \$60,000 for the year. \\
Developer Labor & \$ for the year. \\
Hardware & Each unit with the average number of cameras(4),
cabling, and the computers \$1,500,000\\
Software & \$96,000\\
Licensing & \$1795 \\
Human Resources & \$60,000 for the year.\\
Developer Labor & \$ for the year.\\
\hline
Total & \$ \\
\hline
\end{tabular}

\begin{thebibliography}{9}
    \bibitem{aws} Amazon Web Services (AWS). ``Amazon S3 Pricing.'' AWS, \url{https://aws.amazon.com/s3/pricing/}. Accessed 9 March 2025.
    \bibitem{reolink1} Reolink. ``Security Camera Systems.'' Reolink, \url{https://reolink.com/}. Accessed 9 March 2025.
    \bibitem{reolink2} Reolink. ``5MP IP Security Camera System.'' Reolink, \url{https://reolink.com/blog/5mp-ip-security-camera-system-for-outdoor-use/}. Accessed 9 March 2025.
    \bibitem{raspberrypi} Raspberry Pi Foundation. ``Raspberry Pi 5.'' Raspberry Pi, \url{https://www.raspberrypi.com/}. Accessed 9 March 2025.
    \bibitem{coral} Google Coral. ``Coral USB Accelerator.'' Coral, \url{https://coral.ai/products/accelerator/}. Accessed 9 March 2025.
    \bibitem{tplink} Amazon. ``TP-Link TL-SF1005P 4-Port PoE Switch.'' Amazon, \url{https://www.amazon.com/}. Accessed 9 March 2025.
    \bibitem{netgear} Amazon. ``NETGEAR GS308PP 8-Port PoE Switch.'' Amazon, \url{https://www.amazon.com/}. Accessed 9 March 2025.
    \bibitem{tplink2} Amazon. ``TP-Link TL-SG1016PE 16-Port PoE Switch.'' Amazon, \url{https://www.amazon.com/}. Accessed 9 March 2025.
    \bibitem{deptdirsal} Salary. I.T. Deptartment Director Salary. Salary. \url{https://www.salary.com/research/salary/benchmark/information-technology-director-salary/roanoke-va}
    \bibitem{hdspec} Ziprecruiter. Helpdesk Specialist Salary. Ziprecruiter. \url{https://www.ziprecruiter.com/Salaries/It-Support-Engineer-Salary--in-Virginia#:~:text=How%20much%20does%20an%20It,%2Fweek%20or%20%245%2C442%2Fmonth}
    \bibitem{nsspec} Ziprecruiter. Network Security Specialist Salary. Ziprecruiter. \url{https://www.ziprecruiter.com/Salaries/Network-Security-Engineer-Salary--in-Virginia#:~:text=As%20of%20Feb%2028%2C%202025,%2Fweek%20or%20%2410%2C323%2Fmonth}
    \bibitem{sysadmin} Ziprecruiter. System Administrator Salary. Ziprecruiter. \url{https://www.ziprecruiter.com/Salaries/Systems-Administrator-Salary--in-Virginia}
    \bibitem{sensoftdev} Ziprecruiter. Senior Software Developer Salary. Ziprecruiter. \url{https://www.salary.com/research/salary/alternate/senior-software-engineer-salary/va}
    \bibitem{jrsoftfdev} Ziprecruiter. Junior Software Developer Salary. Ziprecruiter. \url{https://www.ziprecruiter.com/Salaries/Junior-Software-Engineer-Salary--in-Virginia}
    \bibitem{basm} Ziprecruiter. Business Analyst Scrum Master  Salary. Ziprecruiter. \url{https://www.ziprecruiter.com/Jobs/Business-Analyst-Scrum-Master/--in-Virginia?lvk=DzIg93pBUD6xgHsdZitbwQ.--Njl8FSuQB}
\end{thebibliography}

\end{document}